### 2021-09-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@87dc253f76ad2deac20ab4c72ec8ddec6a91188d 🚀

\begin{quote}
Candidates must submit a thesis proposal at least 7 days prior to the
examination. It is the student's responsibility to provide each member
of the Examining Committee with a copy, as well as Ancil Gittens in the
graduate office. The thesis proposal should address the relevant
background, the specific questions to be asked and their significance,
the approach and methods, results already obtained, and the anticipated
schedule. The proposal should be no more than 10 double-spaced pages (12
font). This limit does not include tables, figures, figure legends,
bibliography or the planned timeline to complete work. Committee members
will not be responsible for reviewing text in excess of the page limit.
The written proposal may include preliminary results if available but
must address the whole scope (all chapters) of the projected thesis.\\
The proposal serves two purposes. First, it defines the research area
and thus forms a basis for questioning. Second, it is itself part of the
evidence upon which a final evaluation will be made. For these reasons,
it should be written with care. Please see the additional tips on
proposal writing in the document titled ``QE Expectations and Advice''
(weblink available on Biology Graduate Studies webpage
\end{quote}

@@

\begin{quote}
The student must provide a written proposal for their project to their
QE examining committee at least 7 days prior to the scheduled QE. An
acceptable proposal must be provided at least 7 days in advance or the
QE may need to be rescheduled. It is strongly recommended that a draft
of the proposal be provided to the supervisory committee at least a few
days prior to the supervisory committee meeting mentioned above. This
allows for maximal feedback to be incorporated prior to the QE. The
proposal should be similar in nature to an NSERC grant application
describing the research approach. In general in your proposal and in all
future scientific writing, using subheadings and clear writing to help
the reader is a good idea. The guidelines mandate a proposal of 2500
words (approximately 10 pages double spaced). This limit does not
include tables, figures, bibliography, figure legends, or a planned
timeline to complete work. This 2500 word limit will be enforced. A
proposal of 12 pages might not be rejected (or it might), but a proposal
of 15 pages definitely will. Similarly, the presentation at the start of
the QE is required to be 1520 minutes. This will also be enforced. Both
the written proposal and the oral presentation may include preliminary
results if available but must address the whole of the projected thesis.
- A successful QE will depend heavily on a top-quality proposal. This
proposal should go through multiple drafts and be honed to a very finely
worded document that shows the clarity of your thinking through
conciseness and exact statements. Some topics you should probably cover
are listed below. We recommend discussing omissions from this list with
your advisor and your supervisory committee if you think some of these
sections are not relevant to your particular project. - Brief review of
the current state of knowledge - Precise statement of the question
and/or hypotheses - Description of the methods - Detailed description of
the experimental or sample design. Be clear about what factors are being
controlled or sampled. Provide specific numbers for how many levels of
each factor are planned, and how many replicates/samples within each
factor. Address any issues that arise from finite effort levels in terms
of tradeoffs between replication within vs.~between factors
(i.e.~describe why your plan is optimal). Provide a realistic estimate
of the amount of time this will require in the lab or field. -
Statistical analysis approach. Describe specific statistical approaches,
the output of these approaches, how these can be used to test your
hypotheses, assumptions of the tests, and potential problems. - If you
will be using novel measurement techniques, provide a detailed
description (if you are using standard techniques then references to the
standard techniques are enough). - Provide a description of each chapter
anticipated in the dissertation (this - may be incorporated into the
above sections or as a separate section). - A brief statement of the
broader importance of the question to your field and to society -
Provide a timeline showing when the research and writing will be
performed - (this can be an appendix that does not count against your
\end{quote}

>>>>

\begin{quote}
Candidates must submit a thesis proposal at least 7 days prior to the
examination. It is the student's responsibility to provide each member
of the Examining Committee with a copy, as well as Ancil Gittens in the
graduate office. The thesis proposal should address the relevant
background, the specific questions to be asked and their significance,
the approach and methods, results already obtained, and the anticipated
schedule. The proposal should be no more than 10 double-spaced pages (12
font). This limit does not include tables, figures, figure legends,
bibliography or the planned timeline to complete work. Committee members
will not be responsible for reviewing text in excess of the page limit.
The written proposal may include preliminary results if available but
must address the whole scope (all chapters) of the projected thesis. The
proposal serves two purposes. First, it defines the research area and
thus forms a basis for questioning. Second, it is itself part of the
evidence upon which a final evaluation will be made. For these reasons,
it should be written with care. Please see the additional tips on
proposal writing in the document titled ``QE Expectations and Advice''
(weblink available on Biology Graduate Studies webpage
\end{quote}

@@

\begin{quote}
The student must provide a written proposal for their project to their
QE examining committee at least 7 days prior to the scheduled QE. An
acceptable proposal must be provided at least 7 days in advance or the
QE may need to be rescheduled. It is strongly recommended that a draft
of the proposal be provided to the supervisory committee at least a few
days prior to the supervisory committee meeting mentioned above. This
allows for maximal feedback to be incorporated prior to the QE. The
proposal should be similar in nature to an NSERC grant application
describing the research approach. In general in your proposal and in all
future scientific writing, using subheadings and clear writing to help
the reader is a good idea. The guidelines mandate a proposal of 2500
words (approximately 10 pages double spaced). This limit does not
include tables, figures, bibliography, figure legends, or a planned
timeline to complete work. This 2500 word limit will be enforced. A
proposal of 12 pages might not be rejected (or it might), but a proposal
of 15 pages definitely will. Similarly, the presentation at the start of
the QE is required to be 1520 minutes. This will also be enforced. Both
the written proposal and the oral presentation may include preliminary
results if available but must address the whole of the projected thesis.
- A successful QE will depend heavily on a top-quality proposal. This
proposal should go through multiple drafts and be honed to a very finely
worded document that shows the clarity of your thinking through
conciseness and exact statements. Some topics you should probably cover
are listed below. We recommend discussing omissions from this list with
your advisor and your supervisory committee if you think some of these
sections are not relevant to your particular project. - Brief review of
the current state of knowledge - Precise statement of the question
and/or hypotheses - Description of the methods - Detailed description of
the experimental or sample design. Be clear about what factors are being
controlled or sampled. Provide specific numbers for how many levels of
each factor are planned, and how many replicates/samples within each
factor. Address any issues that arise from finite effort levels in terms
of tradeoffs between replication within vs.~between factors
(i.e.~describe why your plan is optimal). Provide a realistic estimate
of the amount of time this will require in the lab or field. -
Statistical analysis approach. Describe specific statistical approaches,
the output of these approaches, how these can be used to test your
hypotheses, assumptions of the tests, and potential problems. - If you
will be using novel measurement techniques, provide a detailed
description (if you are using standard techniques then references to the
standard techniques are enough). - Provide a description of each chapter
anticipated in the dissertation (this - may be incorporated into the
above sections or as a separate section). - A brief statement of the
broader importance of the question to your field and to society -
Provide a timeline showing when the research and writing will be
performed
\end{quote}
